Figures compiler

### 2017-12-05 analyses/figures-compiler.Rmd
Added individual plots for max/min plots

```{r}
source("../functions/figures_fun.R")
```

@@

>>>>

```{r}
library(ape)
library(dispRity)
source("../functions/figures_fun.R")
```

@@

## Load the data
data_max <- read.csv(paste0("../outputs/peaks.max.", slug, ".csv"), stringsAsFactors = FALSE)

## Get the relative age
relative_time <- read.nexus(file = paste0("../data/processed/tree.", slug, ".tre"))
if(slug == "Wright2017") {
    relative_time <- 484.4
} else {
    relative_time <- max(tree.age(relative_time)$age)
}
```

```{r, fig.width = 12, fig.height = 6}
op <- par(mfrow = c(1,2))
plot.max.min(data_max, relative.time = relative_time, xaxis = TRUE, yaxis = TRUE, pch = 19, main = "Relative age at maximum disparity in Beck2014")
plot.max.min(data_max, relative.time = relative_time, xaxis = TRUE, yaxis = TRUE, pch = 19, main = "Maximum disparity in Beck2014", what = "disparity", legend.coords = "bottomright")
par(op)
```
